\documentclass[margin]{res}
\setlength{\textheight}{10in}
\usepackage{multicol}
\usepackage{hyperref}

\begin{document} 
\name{Logan Campbell}
\address{
  \begin{tabular}{r l}
    0438 050 887 & mail@logaan.net \\
    \href{http://logan.cam/}{logan.cam} & \href{http://github.com/logaan}{github.com/logaan}
  \end{tabular}
}

\begin{resume}                        

  \begin{multicols}{2}
    \section{SKILLS} 
    \textbf{Languages} \\
    Clojure, ClojureScript, Cold Fusion, \\
    Erlang, Golang, Gleam, Grain, Groovy, \\
    Haskell, Java, Javascript, Lua, PHP, \\
    Python, ReasonML, Ruby, Rust, Scala, \\
    VB Script

    \textbf{Frameworks} \\
    Liberator, Reagent, React, Angular, Rails, Spring, Dropwizard, Netty,
    Prototype, YUI, Nitrogen, Alfresco Surf

    \textbf{Tools} \\
    Kubernetes, Kafka, Docker, AWS, Heroku, Postgres, Cassandra, Datomic,
    RabbitMQ \\

    \textbf{Practices} \\
    Scrum, Kanban, Lean, SAFe, TDD, Pair Programming, CI, CD
  \end{multicols}

  \section{EXPERIENCE}

  Block - Afterpay. Melbourne. \\
  Underwriting - Credit Risk team. \\
  Software Engineer - Level 6 IC (Team Leader) Sep 2023 - Mar 2024.
  \begin{itemize}
  \item Lead the back end implementation of Pay As You Go with no payment up
  front
  \end{itemize}

  Zendesk. Melbourne. \\
  Senior Software Engineer. August 2017 - May 2019. \\
  Technical Lead for Apps. Oct 2018 - May 2021. \\
  Staff Software Engineer. May 2019 - March 2022. \\
  Group Technical Lead for Developer Ecosystem. May 2021 - Present. \\
  Senior Staff Software Engineer. March 2022 - Present.
  \begin{itemize}
  \item Evaluation of API Gateways and tender process
  \item Lead the design of tools, standards, and strategy for REST API
    versioning across all of Zendesk (Ruby, Golang, REST)
  \item Design of a request rate monitor and limiter (AWS)
  \item Design and prototypes of a distributed transaction manager (SQS, Ruby,
    Java)
  \item Development of App market (Ruby, Javascript, MySql)
  \end{itemize}

  Silverpond. Melbourne. \\
  Software Engineer.  November 2012 - 2017.
  \begin{itemize}
  \item Physical fault detection model from smart meter readings, API and UI for
    fault analysis and remedy tracking, Power network simulation, and Data
    processing pipeline for Powercor (Python, Clojure, ClojureScript, React)
  \item Training, architecture proposals, and prototyping for Aus Post (Clojure)
  \item Record management interface embedded in a medical device for Bluechiip
    (JS)
  \item Franchisee relationship management UI for 7-Eleven (Clojurescript,
    React)
  \end{itemize} 

  ThoughtWorks. Melbourne. \\
  Consultant Developer.  July 2011 - November 2012.
  \begin{itemize}
  \item Three real time financial web services for IOOF (Java)
  \item Payment consolidation service for NBN (Java)
  \item Charity campaign platform for Live Below The Line (Rails)
  \item Domain registry, and performance test suite for Aus Registry (Java,
    Scala)
  \item Rapidly developed MVP for My Red Alert (Rails)
  \item US political candidate information site for New Organising Institute
    (Rails)
  \item Automated content deployment network for Hitnet (Bash)
  \end{itemize} 

  Hard Hat Digital. South Yarra. \\
  Senior Programmer.  June 2010 to May 2011.
  \begin{itemize}
  \item Implementing HHD's CMS on client websites (Rails)
  \item Publishing open source projects (Rails, Clojure)
  \item Extending HHD's CMS (Rails)
  \item Building custom web applications (Rails)
  \item Maintaining legacy websites (PHP)
  \end{itemize} 

  Curtin University of Technology. Perth. \\
  Web Programmer.  July 2009 to January 2010.
  \begin{itemize}
  \item Developing an Enterprise Document Management System (JS, Alfresco)
  \end{itemize} 

  Webfirm. Perth. \\
  Programmer.  September 2007 to July 2008. \\
  Senior Programmer. July 2008 to July 2009.
  \begin{itemize}
  \item Build app that automated much of my job adding our CMS to client sites
  \item Build app that managed automated deployment of all internal Rails sites
  \item Introduced Rails, trained staff and implemented a new CMS to use with
    Rails
  \item Introduced SVN and then Git, trained staff and set up servers
  \item Rapidly implemented client sites on tight budgets and deadlines
  \end{itemize} 

  Freelance Programmer. 2006-2007.
  
  Personal open source projects available at \href{http://github.com/logaan}{github.com/logaan}

  \begin{multicols}{2}
    \section{TALKS}
    \textbf{EuroClojure 2014} \\
    Clojure at a Post Office

    \textbf{Melbourne FP User Group} \\
    Intro to Erlang, A Monad is not a Burrito, Clojure Workshop, Promise
    Streams, OO values in FP languages, Clojure at a Post Office, Intro to
    Elixir, Full Stack development with FP (Panel)

    \textbf{Melbourne Clojure User Group} \\
    Intro to Datomic, Promise Streams, Async IO Coordination, Nonaga, Squid

    \columnbreak

    \textbf{Australia Post Digital Mailbox} \\
    Async IO Coordination, Clojure Workshop, CQRS with Cassandra

    \textbf{ThoughtWorks Internal Conferences} \\
    Why Functional Programming matters, Introduction to Erlang

    \textbf{Webjam9 2008} \\
    Automated CMS back end website generation
  \end{multicols}

  \section{EDUCATION}
  Monash University, Victoria. \\
  Faculty of Information Technology. \\
  Graduate Certificate of Computer Science. 2024.
  
  Curtin University of Technology, Western Australia. \\
  School of Science, Mathematics and
  Engineering. Department of Computing. \\
  BsC Computer Science. 2005-2007. Did not complete.

  \begin{multicols}{2}
    \section{REFEREES}
    Andrew Buntine, Staff Engineer \\
    Culture Amp, Melbourne \\
    Was my senior at Webfirm and Hard Hat. \\
    info@bunts.io \\
    0423 638 309

	Prakriti Mateti, Director of Engineering \\
	Culture Amp, Melbourne \\
	Was my manager at Zendesk. \\
	itirkarp@gmail.com \\
	0420 801 021
  \end{multicols}

\end{resume} 

\centering
\hspace{-1.75in} The resume is open source, distributed under a modified MIT
License. \\
\hspace{-1.75in} You can find the source code and a copy of the license at
\href{http://github.com/logaan/resume}{github.com/logaan/resume}

\end{document}

